---
title: "Col de la Porte"
output:
  html_document:
    df_print: paged
bibliography: bibliography.bib
---


#### Model: GEOtop v3.0
Compiler: gcc version 4.8.4 (Ubuntu 4.8.4-2ubuntu1~14.04.1) 
Processor: Intel(R) Core(TM) i7-5500U CPU @ 2.40GHz
Author: Stefano Endrizzi (stefano.end@gmail.com),Emanuele Cordano (emanuele.cordano@rendena100.eu)
Date: 25-11-2016

#### Name: ColdelaPorte
Description: Simulation 1D over the Col de la Porte dataset to test the capability of GEOotp to simulate snow depth, snow water equivalent, soil temperature.



#### Results published in:

First result with GEOtop v 2.0 are illustrated in the repot XXX  (@Endrizzi2014 , supplemantary material). 
The following simulated variables have  been tested against observations:

- Snow Height (Snow Dapth);

- Snow Water Equivalent;

- Soil Temperature at 10 cm depth;

- Soil temparature at 20 cm depth;

- Soil Temparature at 50 cm depth;

- Surface Temparature ;

- Albedo .



<!-- - *Endrizzi S., Gruber S., Dall’Amico M., Rigon R., GEOtop 2.0.: Simulating the combined energy and water balance at and below the land surface accounting for soil freezing, snow cover and terrain effects, Geosci. Model Dev., 2014* -->

<!-- ![ColdelaPorte Example Results of GEOtop 2.0 (not reproducible)](images/Geotop-ColDePorte_Endrizzi2014.pdf) -->


#### Observations published in:

see @Morin2012
<!-- - *Morin, S., Lejeune, Y., Lesaffre, B., Panel, J.-M., Poncet, D., David, -->
<!-- P., and Sudul, M.: An 18-yr long (1993–2011) snow and meteorological dataset from a mid-altitude mountain site (Col de Porte, -->
<!-- France, 1325 m alt.) for driving and evaluating snowpack models, Earth Syst. Sci. Data, 4, 13–21, doi:10.5194/essd-4-13-2012, -->
<!-- 2012.* -->

```{r}
plot(cars)
```


#### Simulation duration:


InitDateDDMMYYYYhhmm   = 21/09/2001 00:00
EndDateDDMMYYYYhhmm    = 10/04/2002 00:00

### Output:
PointOutputFile = "output-tabs/surface"


```{r}
library(geotopbricks)
library(magrittr)
library(reshape2)
wpath <- '/home/ecor/activity/2020/geotop_article/git/GEOtopExamples/tests/ColdelaPorte/sims' 
wpaths <- wpath %>% list.files(pattern="sim",full.name=TRUE)
names(wpaths) <- wpath %>% list.files(pattern="sim",full.name=FALSE)
outvar <- c("Tair.C.","Tsurface.C.","snow_depth.mm.","snow_water_equivalent.mm.","SWin.W.m2.","SWbeam.W.m2","SWdiff.W.m2.","SWnet.W.m2.","SWup.W.m2.") 
date_field <- "Date12.DDMMYYYYhhmm."
tz <- "Etc/GMT-1"

get_out <- function(wpath,outvar=outvar,...){  
  
  o <- get.geotop.inpts.keyword.value("PointOutputFile",data.frame=TRUE,wpath=wpath,...)
  tt <<- get.geotop.inpts.keyword.value("SoilAveragedTempProfileFile",data.frame=TRUE,wpath=wpath,zlayer.formatter="z%04d",...)   ###SoilAveragedTempProfileFile 
  ###
  
  stop("HERE")
   o <- o[,outvar]
   ## zoo to dataframe
   nn <- names(o)
   time <- index(o)
   o <- as.data.frame(o)
   o$time <- as.POSIXct(time)
   ###index(o) <- NULL
   o <-o[,c("time",nn)]
   oo <- o
   return(o)
}
##out_v2 <- wpaths %>% lapply(FUN=get_out,add_suffix_dir="_v2",outvar=outvar)
out_v3 <- wpaths %>% lapply(FUN=get_out,add_suffix_dir="_v3",outvar=outvar,date_field=date_field,tz=tz) %>% melt(id="time")

stop("HERE")
#out <-"PointOutputFile" %>% mapply(FUN=get.geotop.inpts.keyword.value,wpath=wpaths,SIMPLIFY = FALSE,data.frame=TRUE) 


knitr::kable(out_v3[1000+100:105,])

```
```{r} 
library(ggplot2)
library(dplyr)
varname <- "snow_depth.mm."
out <- out_v3 %>% filter(variable==varname)
g <- ggplot()+geom_line(aes(x=time,y=value,group=L1,col=L1),data=out)+theme_bw()
g
```





### Observations:
Snow heigth mm, Snow Water Equivalent mm, T surface C, T soil 10cm C,T soil 20cm C,T soil 50cm C







### References

```{r generateBibliography,echo=FALSE,eval=TRUE,message=FALSE,warning=FALSE,print=FALSE,results="hide"}
require("knitcitations")
cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "bibliography.bib")

